\chapter*{Acknowledgements}
\markboth{Acknowledgements}{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}

\vspace*{\fill}

First of all, I am grateful that Pierre Vandergheynst accepted me into his group (LTS2) and had the insight to propose a research topic that would keep me interested, and busy, for years. Thank you in particular for encouraging me to go to any conference I was drawn to, even if I had no work to present there.

\vspace*{\fill}

At LTS2, my colleagues could not have been more welcoming. Benjamin Ricaud and Xavier Bresson were fundamental in introducing me to research life. Andreas Loukas became the source for discussing theory, and the ideal partner for playing questionable, but heartfelt, Flight of the Conchords covers. Through ups and downs, the Ph.D. students of LTS2 developed a good sense of comradery. I will not disclose, however, how much of this development involved table football. Listing everyone from LTS2, and neighboring groups, who helped me go through my doctoral studies would fill most of this page, but I thank you all for the time we shared.

\vspace*{\fill}

Most of my Ph.D. was funded by the European Union's FP7-PEOPLE-2013-ITN program under grant agreement n\textsuperscript{o} 607290 SpaRTaN. While I do appreciate the money, I would like to mostly thank the \emph{people} from  SpaRTaN and its partner network, MacSeNet. We learned together and we laughed together, and I believe we are all better-off for having met one another. Especial thanks go to everyone at the CVSSP in the University of Surrey and at the Fraunhofer IDMT for hosting me.

\vspace*{\fill}

Much to my family's fault, I consider a life in pursuit of education to be a noble endeavor. Often when surrounded by books I am transported back home. I know that being nine thousand kilometers apart is hard on us, so I appreciate your support. My grandfather, being an immigrant himself, told me upon my moving that I now ``belonged to the world''. I agree, but I also believe in visiting for coffee and loud conversations around the table.

\vspace*{\fill}

Lastly, and most importantly, I would like to thank my wife and confidante extraordinaire, Anna. She was a published author years before me, but never bragged about it. Anna lifted my mood when I had a hard time putting thoughts to paper; she will probably continue doing so long after I forget what I wrote here. This work is dedicated to you.

\vspace*{\fill}

\emph{Lausanne, 30 September 2019 \hfill R.~C.~G.~P.}
